---
title: "OptiVisT AIBox Grasping Task Analysis"
author: "Florian Pätzold"
date: "12/09/2024"
output:
  html_document: default
  pdf_document: default
---

# 1. Setup

Set up the document.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
#knitr::opts_chunk$set(echo = TRUE, message = TRUE, warning = TRUE) # for debugging
```

Import all necessary packages.

```{r, echo=FALSE}
library(tidyverse) # ggplot2, tibble, tidyr, readr, purrr, dplyr, stringr, forcats
library(scales) # ggplot default color palette
library(e1071) # skewness and kurtosis
```

Load all the grasping data.

```{r}
# Set working directory to the folder containing the CSV files
base_dir <- getwd()
data_dir <- paste0(base_dir, "/../data/")

# Get list of all CSV files for the grasping task in the folder
files <- list.files(data_dir, pattern = "*grasping_task*")

data_raw <- data.frame()
for (file in files) {
  csv_data <- read_csv(paste0(data_dir,file))
  participant_id = str_sub(file, start = -5, end = -5)
  csv_data <- csv_data %>% mutate(participant_id = as.numeric(participant_id))
  data_raw <- rbind(data_raw, csv_data)
}

# View sample of the combined data
data_raw %>% sample_n(10)

# Save the combined data frame as a CSV file
write.csv(data_raw, paste0(data_dir,"combined_grasping.csv"), row.names = FALSE)
```

# 2. Data Preprocessing

## 2.1 Data Engineering

Rename the columns and set data type.

```{r}
coco_labels <- c(
  "person", "bicycle", "car", "motorcycle", "airplane", "bus", "train", "truck", "boat",
  "traffic light", "fire hydrant", "stop sign", "parking meter", "bench", "bird", "cat", 
  "dog", "horse", "sheep", "cow", "elephant", "bear", "zebra", "giraffe", "backpack", 
  "umbrella", "handbag", "tie", "suitcase", "frisbee", "skis", "snowboard", "sports ball", 
  "kite", "baseball bat", "baseball glove", "skateboard", "surfboard", "tennis racket", 
  "bottle", "wine glass", "cup", "fork", "knife", "spoon", "bowl", "banana", "apple", 
  "sandwich", "orange", "broccoli", "carrot", "hot dog", "pizza", "donut", "cake", "chair", 
  "couch", "potted plant", "bed", "dining table", "toilet", "tv", "laptop", "mouse", "remote", 
  "keyboard", "cell phone", "microwave", "oven", "toaster", "sink", "refrigerator", "book", 
  "clock", "vase", "scissors", "teddy bear", "hair drier", "toothbrush"
)
names(coco_labels) <- as.character(0:79)

data_engineered <- data_raw %>% 
  mutate(trial = as.numeric(...1),
         object = coco_labels[as.character(`0`)],
         duration = as.numeric(`1`),
         success = as.numeric(ifelse(`2` == "y",1,0))
         ) %>% 
  select(participant_id, trial, object, duration, success)

# View sample of the engineered data
data_engineered %>% sample_n(10)
```

## 2.2 Data Cleaning

We will detect and treat missing values as well as technical false measurements.

```{r}
n_uncleaned <- nrow(data_engineered)

# Detect missing values and outliers
outliers <- rbind(
  data_engineered %>% filter(!complete.cases(.)), 
  data_engineered %>% filter_all(all_vars(is.infinite(.))),
  data_engineered %>% filter(participant_id < 0), # No negative participant IDs
  data_engineered %>% filter(trial < 0), # No negative trial numbers
  data_engineered %>% filter(trial > 25), # Grasping task has exactly 25 trials
  data_engineered %>% filter(duration < 0), # Negative trial durations are measuring error
  data_engineered %>% filter(success != 0 & success != 1)
  )
outliers

# Treatment
data <- data_engineered %>% anti_join(outliers, by = colnames(data_engineered))

n_cleaned <- nrow(data)
cat('Rows removed: ', n_uncleaned - n_cleaned)
```

Outlier detection and potential treatment. Here, only the duration is of relevance.

```{r}
# Visualize duration distribution
data %>% 
  ggplot(aes(x = duration, fill = participant_id)) +
  geom_density(alpha=0.4) +
  labs(title = "Duration distribution by Participant\n",
       x = "\nDuration",
       y = NULL) +
  theme_minimal()

# Visualize normality using QQ-plot
data %>% 
  ggplot(aes(sample = duration)) +
  geom_qq() +
  geom_qq_line(color = 'firebrick') +
  labs(title = "Q-Q Plots of Duration by Participant\n",
       x = "\nTheoretical Quantiles",
       y = "Sample Quantiles\n") +
  theme_minimal() +
  facet_wrap(~ participant_id)

# Summary statistics for duration
data %>% 
  group_by(participant_id) %>% 
  summarise(
    min = min(duration), 
    median = median(duration), 
    mean = mean(duration), 
    max = max(duration), 
    skew = skewness(duration)
    )

# Optional: Shapiro-Wilk Test (Wilhelm, Jochen. (2020). Re: Use T test, transform data or use non parametric tests?. Retrieved from: https://www.researchgate.net/post/Use_T_test_transform_data_or_use_non_parametric_tests/5efd860f4397bc39891a1b98/citation/download. )

# Treatment: natural slight right-skewness [0,Inf] --> no treatment
```

The data is slightly right-skewed, but neither strongly nor extremely, so this is acceptable.

# 3. Analysis

## 3.1 Exploration

### Visualizations

We will explore the data using visualizations and summary statistics.

Pre-load color palette.

```{r}
hex <- hue_pal()(8)
hex
show_col(hex)

# red: #F8766D
# orange: #C49A00
# olive: #93AA00
# green: #00BE67
# cyan: #00BFC4
# lightblue: #00B9E3
# darkblue: #619CFF
```

Performance over time (fatigue effects)

```{r}
# Trial durations over time (speed fatigue)
data %>% group_by(trial) %>% summarise(mean_duration = mean(duration)) %>% 
  ggplot(aes(x = trial, y = mean_duration)) +
  geom_point(color = '#F8766D') +
  geom_line(color = '#F8766D') +
  labs(title = "Mean Duration per Trial\n",
       x = "\nTrial",
       y = "Duration\n") +
  theme_minimal()

# Success rates over time (accuracy fatigue)
success_freq <- data %>% group_by(trial) %>% summarise(success_count = sum(success == 1))
n_participants <- max(data$participant_id)
success_freq %>% 
  ggplot(aes(x = trial, y = (success_count/n_participants)*100)) +
  geom_col(fill = '#00BFC4') +
  labs(title = "Success Percentage per Trial\n",
       x = "\nTrial",
       y = "Success Percentage\n") +
  scale_y_continuous(
    breaks = c(seq(from = 0, to = 100, by = 20)),
    limits = c(0, 100)
    ) +
  theme_minimal()
```

Inidividual performance differences.

```{r}
# Differences between participants in trial duration
data %>% 
  ggplot(aes(x = participant_id, y = duration)) +
  geom_boxplot(fill = '#619CFF') +
  labs(title = "Title\n",
       x = "\nParticipant",
       y = "Duration\n") +
  theme_minimal()

# Differences between participants in success rates
n_trials <- max(data$trial)
data %>%
  group_by(participant_id) %>%
  summarize(success_count = sum(success == 1)) %>%
  ggplot(aes(x = as.factor(participant_id), y = (success_count/n_trials)*100)) +
  geom_col(color = 'black', fill = '#C49A00') +
  geom_text(aes(label = round((success_count/n_trials)*100, 2), vjust = 2)) +
  labs(title = "Success Rate per Participant\n",
       x = "\nParticipant",
       y = "Success Percentage\n") +
  scale_y_continuous(
    breaks = c(seq(from = 0, to = 100, by = 20)),
    limits = c(0, 100)
    ) +
  theme_minimal()
```

### Correlation

We will now investigate potential correlations between variables.

```{r}

```


## 3.2 Confirmation

After EDA, we will formulate and test relevant hypotheses.

```{r}

```


# 4. Modeling

Not required.


